---
title: "Id Inf"
output: html_document
---

```{r}
library(dplyr)
library(ggplot2)
library(readr)
library(here)
library(pryr)
```

```{r}
reads_clinical <- read_tsv(here("retained-NR.retained-NT.filter.unmapped.cdhit.ZINTER_TRIZ_100K_CFU.1.m8.lca_forJB"))
reads_mb <- read_tsv(here("SRR172902-FAUHGnt-n1000.m8.v2_forJB"))
```

The clinical sample has 1.5 m reads with 1.7 m mappings to 4k species.

The microbiome sample has 3 m reads with 13 m mappings to 34k species.

```{r}
dim(reads_mb)
length(unique(reads_mb$qseqid))
length(unique(reads_mb$tax_id))
dim(reads_clinical)
length(unique(reads_clinical$qseqid))
length(unique(reads_clinical$tax_id))
```

There are 3697 species involved. That many equations may be somewhat unpleasant to solve. It is likely that the problem will split (as with FLASH). If each read gives a multiedge in a graph, connecting many species, then (ratios) of species in each component of that graph can be determined independently. Doing this will be easier in python, where I know the sparse matrix libraries.

```{r}
reads_clinical %>% group_by(qseqid) %>% summarize(mappings = n()) %>% ggplot(aes(x = mappings)) + geom_histogram(bins = 10) + scale_y_log10()
```

```{r}
reads_mb %>% group_by(qseqid) %>% summarize(mappings = n()) %>% ggplot(aes(x = mappings)) + geom_histogram(bins = 10) + scale_y_log10()
```

Bitscore distribution

```{r}
reads_clinical %>% ggplot(aes(x = bitscore)) + geom_histogram()
```

